Personality and political beliefs across the lifespan

### 2019-11-27 scripts/manuscript.Rmd
script feedback

#Openness to experiences
scaleKey <- c(0, 0, 0, 0, 5, 0, 0, 0, 0, -1)
open <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 1, max = 7)
data <- data %>% 
  mutate(Openness_to_experiences = open$scores[,1])
```

```{r select}
#selecting the variables that we want to use, cleaning, and characterizing dataset
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize() %>% 
  mutate(age = as.numeric(age))
```

>>>>

#Openness to experiences
scaleKey <- c(0, 0, 0, 0, 5, 0, 0, 0, 0, -1)
open <- scoreItems(keys = scaleKey, items = data[items], 
  totals = FALSE, missing = FALSE, min = 1, max = 7)
data <- data %>% 
  mutate(Openness_to_experiences = open$scores[,1])

```{r select}
#selecting the variables that we want to use, cleaning, and characterizing dataset
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize() %>% 
  mutate(age = as.numeric(age))

#Are you going to include the ethnicity data in later plots? If not, you could just select the other columns. 
```
